---
title: "gabovicen_OriginalHomeworkCode_04"
author: "Gabriel Vicencio"
date: "11/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library(curl)
library(tidyverse)
library(boot)
```


```{r}
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN588_Fall21/KamilarAndCooperData.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
```
```{r}
names(d)
```



## [1] Using the “KamilarAndCooperData.csv” dataset, run a linear regression looking at log(HomeRange_km2) in relation to log(Body_mass_female_mean) and report your β coeffiecients (slope and intercept).

```{r}
x <- log(d$Body_mass_female_mean)
y <- log(d$HomeRange_km2)

lr <- lm (y ~ x, data = d)
summary(lr)
```

```{r}
r <- coef(summary(lr))
r <- data.frame(unlist(r))
r

beta0 <- r$Estimate[1]
beta0

beta1 <- r$Estimate[2]
beta1

```

## [2] Then, use bootstrapping to sample from your data 1000 times with replacement, each time fitting the same model and calculating the same coefficients. This generates a sampling distribution for each β coefficient.


```{r}
k1 <- function(formula, data, indices) {
  
  dt <- data[indices,]
  m2 <- lm(formula, data = dt)
  return(coef(m2))
}
```

```{r}
library(boot)

bootobject <- boot(data = d, statistic = k1, R = 1000, formula = log(HomeRange_km2) ~ log(Body_mass_female_mean))
```

##https://www.statmethods.net/advstats/bootstrapping.html

```{r}
plot(bootobject, index = 1)
plot(bootobject, index = 2)
```

```{r}
boot.ci(bootobject, conf = 0.95, index = 1, type = "norm") 
boot.ci(bootobject, conf = 0.95, index = 2, type = "norm")
```

*call on your boot object to look t the stats the questions ask about*
